The Dynamics of Anthropomorphism in Human-Robot Interaction

### 2014-04-04 paper.tex
Re-organize section hierarchy in Section 3

\paragraph{Artifact-centered perspective on anthropomorphism\\}

@@

\paragraph{Human-centered perspective on anthropomorphism\\}

@@

\subsection{Developmental psychology research on the attribution of animacy and intention}
\label{sec:developmental-expl}

@@

\subsection{Cognitive science research, the mental model theory (Theory of Mind)
and neural correlates of anthropomorphism}
\label{sec:cognitive-expl}

@@

\subsection{Social psychology research: a 3-factor theory of anthropomorphism}
\label{sec:psychological-factors}

>>>>

\subsection{Artifact-centered perspective on anthropomorphism}

@@

\subsection{Human-centered perspective on anthropomorphism}

@@

\subsubsection{Developmental psychology research on the attribution of animacy and intention}
\label{sec:developmental-expl}

@@

\subsubsection{Cognitive science research, the mental model theory (Theory of Mind)
and neural correlates of anthropomorphism}
\label{sec:cognitive-expl}

@@

\subsubsection{Social psychology research: a 3-factor theory of anthropomorphism}
\label{sec:psychological-factors}
